---
title       : Predicting Wine Prices
subtitle    : Data Analysis as the New Wine Expert !
author      : Metin Turgal
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Statistics vs. Wine Expert 

1. Orley Ashenfelter, a Princeton economics professor, shows that a statistical analysis can outperform wine experts on predicting quality wine.
2. He has used linear regression with the following features to predict the price 
 + Age (older wines are more expensive)
 + Average Growing Season Temperature
 + Harvest Rain
 + Winter Rain
3. The same method and the data is used for our prediction tool, "Wine Price Prediction" website 

---
## The Model
+ The variables on which the prediction is based on are statistically powerful predictors,as shown below:
```{r echo=FALSE}
wine <- read.csv("C:/Users/mturgal/Documents/KISISEL/PROGRAMCILIK/Data Science/9_Developing Data Products/wine.csv")
```

```{r}

summary(lm(Price~AGST+HarvestRain+ WinterRain+Age,data=wine))

```

---
## Model Variables vs. Wine Price

```{r echo=FALSE}
par (mfrow= c (2,2))
plot(Price~Age,data=wine, xlab="Age of Wine (Years)",pch=16)
abline(lm(Price~Age,data=wine))
plot(Price~AGST,data=wine, xlab="Avg Growing Season Temp(Celsius)",pch=16)
abline(lm(Price~AGST,data=wine))
plot(Price~HarvestRain,data=wine, xlab="Harvest Rain(mm)",pch=16)
abline(lm(Price~HarvestRain,data=wine))
plot(Price~WinterRain,data=wine, xlab="Winter Rain(mm)",pch=16)
abline(lm(Price~WinterRain,data=wine))

```

---

## Why Should You Consider It ?

1. It's cheaper than hiring a wine expert.
2. It's convenient : Even from your mobile device you can get a prediction. 
3. It's fast: It doesn't need a time a preliminary research. It is already done ! 
4. Simple and straightforward 
 + It doesn't need any prior knowledge, it can be used easily by anybody.
 

